---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
#install.packages('bench')
#library(bench)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mypackage.lm)
```


### Description

`LM` is a function that is designed to perform the fitting of linear regression models, 
which gives the essential fitted values and related results from a fitted linear regression model. 
`summaryLM()` is a function that prints the summary of the output from `LM`. The default data set  `iris` is used for examples and tutorials. 

### Usage of function `LM()` and `summaryLM()`:

In this section, we introduce the usage of `LM` and `summaryLM()`.  

#### Call the function `LM()` and obtain the related fitted values and results 

For example, we can obtain the $R^2$ and  $R^2_{adj}$ for the fitted model, as well as the fitted coefficients and corresponding t-test results as follow: 
```{r}
LM_result = LM(Sepal.Width ~ Sepal.Length + Petal.Length, data = iris)
LM_result$r.squared
LM_result$adj.r.squared
LM_result$coefficients_df
```

All the related results include: coefficients, residuals, rank, fitted.values, df.residual, model, call, terms, coefficients_df, sigma, r.squared, adj.r.squared, fstatistic, F.p-value, cov.unscaled. These variables can all be called by the format of `LM_result$variable_name`. 

#### Call the function `LM()` and use `summaryLM()` to print the output    

`summaryLM()` provides a printed summary of outputs/related fitted results of the fitted linear regression model. 
```{r}
summaryLM(LM(Sepal.Width ~ Sepal.Length + Petal.Width, data = iris))
```


#### Two ways to include interaction 
  
1.  Using * includes main effects and interaction 
```{r}
LM(Sepal.Width ~ Sepal.Length * Petal.Length, data = iris)
```
  
2. Using I includes only the interaction and omits main effects
```{r}
LM(Sepal.Width ~ I(Sepal.Length * Petal.Length), data = iris)
```

#### Fit linear regression model without intercept 

Add -1 in the formula to represent without intercept. 
```{r}
LM(Sepal.Width ~ -1 + Sepal.Length + Petal.Width, data = iris)
```


### Correctness and Efficiency(Benchmark): `LM()` against `lm()` and `summary(lm())`:
Both the build-in methods `lm` and `summary(lm)` returns the related results from a fitted linear regression model, but each method would return different kinds of results. However, the function `LM` combine those results, which includes the essential results from both methods. 

Therefore, in this section, we compare the outputs of `LM()` against build-in method `lm` and `summary(lm())`. 

We use `LM()` and `lm()` to fit the same model and compare both correctness and efficiency. 
```{r}
LM_result = LM(Sepal.Width ~ Sepal.Length + Petal.Length, data = iris)
lm_result = lm(Sepal.Width ~ Sepal.Length + Petal.Length, data = iris)
lm_summary_result = summary(lm_result)
```

#### Coefficients
```{r}
all.equal(LM_result$coefficients, lm_result$coefficients) 
#mark(LM_result$coefficients, lm_result$coefficients)
```

#### Residuals
```{r}
all.equal(LM_result$residuals, lm_result$residuals) 
#mark(LM_result$residuals, lm_result$residuals)
```

#### Rank 
```{r}
all.equal(LM_result$rank, lm_result$rank) 
#mark(LM_result$rank, lm_result$rank)
```

#### Fitted values
```{r}
all.equal(LM_result$fitted.values, lm_result$fitted.values) 
#mark(LM_result$fitted.values, lm_result$fitted.values)
```

#### Degree of freedom of Residual
```{r}
all.equal(LM_result$df.residual, lm_result$df.residual) 
#mark(LM_result$df.residual, lm_result$df.residual)
```

#### Model
```{r}
all.equal(as.matrix(LM_result$model), as.matrix(lm_result$model))
#mark(as.matrix(LM_result$model), as.matrix(lm_result$model))
```

#### Sigma
```{r}
all.equal(LM_result$sigma, lm_summary_result$sigma) 
#mark(LM_result$sigma, lm_summary_result$sigma)
```

#### $R^2$
```{r}
all.equal(LM_result$r.squared, lm_summary_result$r.squared) 
#mark(LM_result$r.squared, lm_summary_result$r.squared)
```

#### $R_{adj}^2$
```{r}
all.equal(LM_result$adj.r.squared, lm_summary_result$adj.r.squared) 
#mark(LM_result$adj.r.squared, lm_summary_result$adj.r.squared)
```

#### F statistics and P values 
```{r}
all.equal(LM_result$fstatistic, lm_summary_result$fstatistic) 
#mark(LM_result$fstatistic, lm_summary_result$fstatistic)
```


#### Unscaled Covariance
```{r}
all.equal(LM_result$cov.unscaled, lm_summary_result$cov.unscaled) 
#mark(LM_result$cov.unscaled, lm_summary_result$cov.unscaled)
```





