---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(stats)
library(bench)
library(ggbeeswarm)
library(tidyr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mypackage.lm)
```


### Description

`LM` is a function that is designed to perform the fitting of linear regression models, 
which gives the essential fitted values and related results from a fitted linear regression model. 
`summaryLM()` is a function that prints the summary of the outputs from `LM()`. 

Note: The `R`'s default dataset `iris` is used for examples and tutorials. 

### Usage of function `LM()` and `summaryLM()`:

In this section, we introduce the usage of `LM()` and `summaryLM()`.  

#### Call the function `LM()` and obtain the outputs relate to the fitted model using `$` followed by its name

```{r}
## fit a multiple linear regression model
LM_result = LM(Sepal.Width ~ Sepal.Length + Petal.Width, data = iris)
LM_result$coefficients
LM_result$residuals
LM_result$rank
LM_result$fitted.values
LM_result$df.residual
LM_result$call
LM_result$terms
LM_result$coefficients_df
LM_result$sigma
LM_result$r.squared
LM_result$adj.r.squared
LM_result$fstatistic
LM_result$`F.p-value`
LM_result$cov.unscaled
```

All the related results include: coefficients, residuals, rank, fitted.values, df.residual, model, call, terms, coefficients_df, sigma, r.squared, adj.r.squared, fstatistic, F.p-value, cov.unscaled. These variables can all be called by the format of `LM_result$variable_name`. 

#### Call the function `LM()` and use `summaryLM()` to print the outputs    

`summaryLM()` provides a printed summary of outputs/related fitted results of the fitted linear regression model:
```{r}
summaryLM(LM(Sepal.Width ~ Sepal.Length + Petal.Width, data = iris))
```

#### Fit a simple linear regression model
```{r}
LM_result = LM(Sepal.Width ~ Sepal.Length, data = iris)
summaryLM(LM_result)
```

#### Fit a linear regression model without intercept 
```{r}
LM_result = LM(Sepal.Width ~ Sepal.Length + Petal.Width, data = iris, intercept = FALSE)
summaryLM(LM_result)
```

#### About adding interaction terms
  
1. Using * includes main effects and interaction:
```{r}
LM(Sepal.Width ~ Sepal.Length * Petal.Length, data = iris)
```
  
2. Using I omits main effects and includes only the interaction:
```{r}
LM(Sepal.Width ~ I(Sepal.Length * Petal.Length), data = iris)
```



### Correctness and Efficiency(Benchmark): `LM()` against `lm()` and `summary(lm())`:
Both the build-in methods `lm()` and `summary(lm())` returns the related results from a fitted linear regression model by using `$`, but each method would return different kinds of results. Therefore, the function `LM()` combine those results, that is to include the essential results from both methods. 

In this section, we compare the outputs of `LM()` against build-in method `lm()` and `summary(lm())`. 

We use `LM()` and `lm()` and `summary(lm())` to fit the same model and compare both correctness and efficiency.
By comparing all the returned essential values related to the fitted model, we see they are equivalent. 
Note that we use the default dataset `iris` in R to obtain the following results. 

```{r}
LM_result = LM(Sepal.Width ~ Sepal.Length + Petal.Length, data = iris)
lm_result = lm(Sepal.Width ~ Sepal.Length + Petal.Length, data = iris)
lm_summary_result = summary(lm_result)
```

#### Compare: Coefficients
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
library(bench)
all.equal(LM_result$coefficients, lm_result$coefficients) 
mark(LM_result$coefficients, lm_result$coefficients)
plot(mark(LM_result$coefficients, lm_result$coefficients))
```

#### Compare: Residuals
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
all.equal(LM_result$residuals, lm_result$residuals) 
mark(LM_result$residuals, lm_result$residuals)
plot(mark(LM_result$residuals, lm_result$residuals))
```

#### Compare: Rank 
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
all.equal(LM_result$rank, lm_result$rank) 
mark(LM_result$rank, lm_result$rank)
plot(mark(LM_result$rank, lm_result$rank))
```

#### Compare: Fitted values
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
all.equal(LM_result$fitted.values, lm_result$fitted.values) 
mark(LM_result$fitted.values, lm_result$fitted.values)
plot(mark(LM_result$fitted.values, lm_result$fitted.values))
```

#### Compare: Degree of freedom of Residual
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
all.equal(LM_result$df.residual, lm_result$df.residual) 
mark(LM_result$df.residual, lm_result$df.residual)
plot(mark(LM_result$df.residual, lm_result$df.residual))
```

#### Compare: Sigma
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
all.equal(LM_result$sigma, lm_summary_result$sigma) 
mark(LM_result$sigma, lm_summary_result$sigma)
plot(mark(LM_result$sigma, lm_summary_result$sigma))
```

#### Compare: $R^2$
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
all.equal(LM_result$r.squared, lm_summary_result$r.squared) 
mark(LM_result$r.squared, lm_summary_result$r.squared)
plot(mark(LM_result$r.squared, lm_summary_result$r.squared))
```

#### Compare: $R_{adj}^2$
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
all.equal(LM_result$adj.r.squared, lm_summary_result$adj.r.squared) 
mark(LM_result$adj.r.squared, lm_summary_result$adj.r.squared)
plot(mark(LM_result$adj.r.squared, lm_summary_result$adj.r.squared))
```

#### Compare: F statistics and P values 
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
all.equal(LM_result$fstatistic, lm_summary_result$fstatistic) 
mark(LM_result$fstatistic, lm_summary_result$fstatistic)
plot(mark(LM_result$fstatistic, lm_summary_result$fstatistic))
```


#### Compare: Unscaled Variance-Covariance matrix
```{r fig.align ='center', fig.width= 5, fig.height = 1.5, message=FALSE}
all.equal(LM_result$cov.unscaled, lm_summary_result$cov.unscaled) 
mark(LM_result$cov.unscaled, lm_summary_result$cov.unscaled)
plot(mark(LM_result$cov.unscaled, lm_summary_result$cov.unscaled))
```





